SPIN Novelty Data

### 2019-08-21 stats/kids_basic_me.Rmd
add combination data

files <- dir("~/Work/Spin/raw_data/kids/basic_me/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,44,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

length(unique(raw_data$subid))

d_raw <-raw_data %>%
  mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
         subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
         subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
         subage = ifelse(subid == "190313_5_me", "3",subage),
         test_date = as.Date(test_date))

log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
  filter(Condition == "me")%>%
  mutate(dob = as.character(dob),
         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
         dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
         dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
         dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

d_raw%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

write_csv(d, "../data/child_basic_me.csv")
```

@@

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
```

>>>>

# files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,44,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# 
# length(unique(raw_data$subid))
#  
# d_raw <-raw_data %>%
#   mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
#          subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
#          subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
#          subage = ifelse(subid == "190313_5_me", "3",subage),
#          test_date = as.Date(test_date))
# 
# 
# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
#   filter(Condition == "me")%>%
#   mutate(dob = as.character(dob),
#          dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
#          dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
#          dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
#          dob = as.Date(dob))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
#  
# d_raw%>%
#   group_by(subid)%>%
#   summarise(n())%>%
#   filter(!(subid %in% unique(log$subid)))
# 
#  
# d <- left_join(d_raw,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
# 
# write_csv(d, "../data/me.csv")

d <- read_csv("../data/me.csv")%>%
  mutate(subage = factor(subage))
```

@@

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

ggsave("../graphs/me_by_item.png", width = 6, height = 3, scale = 1.2)
```

### 2019-08-21 stats/kids_combination.Rmd
add combination data

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/Spin/raw_data/kids/combination/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,56,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data %>%
  mutate(discourseNovel = str_sub(discourseNovel,11),
         mutExNovel = str_sub(mutExNovel, 10))

@@

>>>>

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(brms)

## importing data
# files <- dir("~/Work/Spin/raw_data/kids/combination/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,56,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# d_raw <- raw_data %>%
#   mutate(discourseNovel = str_sub(discourseNovel,11),
#          mutExNovel = str_sub(mutExNovel, 10),
#          subid = ifelse(subid == "190726_6_come", "190726_6_com", subid))
# 
# d_raw %>%
#   filter(subid == "190727_1_com")
# 
# 
# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
#   filter(Condition == "com")%>%
#   mutate(dob = as.character(dob),
# #         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
#          dob = as.Date(dob))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
#  
# d_raw%>%
#   group_by(subid)%>%
#   summarise(n())%>%
#   filter(!(subid %in% unique(log$subid)))
# 
#  
# d <- left_join(d_raw,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
# 
# 
# write_csv(d, "../data/combination.csv")

d <- read_csv("../data/combination.csv")%>%
  mutate(subage = factor(subage))

@@

```{r}
aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% d$familiarObject )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         familiarObject = Word)%>%
  select(familiarObject,mean_aoa)
```

```{r}
d %>%
  filter(condition != "train")%>%
  group_by(condition,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())
```

```{r plot by numerical age, echo = F}
p2 <- d %>%
  filter(condition != "train")%>%
    left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiarObject = fct_reorder(factor(familiarObject), mean_aoa))

ggplot(data = p2, aes(x = age_num, y = correct, col = familiarObject, fill = familiarObject)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~condition)+
  #ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
```

```{r plot by age, echo= FALSE}
p1 <- d %>%
  filter(condition != "train")%>%
  group_by(subage, familiarObject,condition) %>%
  multi_boot_standard(col = "correct")%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(familiarObject = fct_reorder(factor(familiarObject), mean_aoa))

ggplot(data = p1, aes(x = familiarObject, y = mean, group=1, col = subage)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),size = .8)+
  stat_summary(aes(group = subage, col = subage),fun.y=mean, geom="line")+
  labs(x="",y="Proportion Correct")+
  facet_grid(condition~.)+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_colour_solarized()
```

```{r}
d_model <- d %>%
  filter(condition != "train")%>%
  left_join(aoa_ratings)%>%
  mutate(age_num = age_num - mean(age_num),
         aoa = mean_aoa- mean(mean_aoa))

model <- brm(correct ~ familiarObject * age_num * condition,
                    data = d_model, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)

summary(model)

plot(model)

### 2019-08-21 stats/kids_novelty.Rmd
add combination data

files <- dir("~/Work/Spin/raw_data/kids/novelty/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/novelty/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,46,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

length(unique(raw_data$subid))

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date),
         subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
         subage = ifelse(subid =="190422_2_nov","4",subage))

log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
  filter(Condition == "nov")%>%
  mutate(dob = as.character(dob),
         dob = ifelse(subid =="190502_9_nov","2016-10-08",dob),
         dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

d_raw%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  select(-pick_src)

## import mcc data

files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")

raw_data_mcc <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,51,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data_mcc <- bind_rows(raw_data_mcc, id)
}

d_raw_mcc <-raw_data_mcc %>%
  mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
         test_date = as.Date(test_date))

log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "nov")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         leftObject = leftFruit,
         rightObject = rightFruit, 
         pick = str_sub(pick,72,str_length(pick)-4),
         agent = ifelse(speakerChange == "false", agent,altAgent),
         experiment = "dis_novelty_mcc")%>%
  filter(speakerChange == "false", trial != "train")%>%
  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)

# join datasets

d <- bind_rows(d_spin, d_mcc)

write_csv(d_spin, "../data/child_spin_novelty.csv")
write_csv(d, "../data/child_novelty.csv")
```

@@

d <- read_csv("../data/child_novelty.csv")%>%
  mutate(subage = factor(subage))

@@

ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
  geom_smooth(data = d_spin, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.01)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion novel item chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

>>>>

# files <- dir("~/Work/Spin/raw_data/kids/novelty/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/Spin/raw_data/kids/novelty/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,46,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# 
# length(unique(raw_data$subid))
# 
# d_raw <-raw_data %>%
#   mutate(test_date = as.Date(test_date),
#          subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
#          subage = ifelse(subid =="190422_2_nov","4",subage))
# 
# 
# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.character(dob),
#          dob = ifelse(subid =="190502_9_nov","2016-10-08",dob),
#          dob = as.Date(dob))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# d_raw%>%
#   group_by(subid)%>%
#   summarise(n())%>%
#   filter(!(subid %in% unique(log$subid)))
# 
#  
# d_spin <- left_join(d_raw,log, by = "subid")%>%
#   filter(keep_drop == "keep",
#          trial != "train1", trial != "train2")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          experiment = condition)%>%
#   select(-pick_src)
# 
# 
# ## import mcc data
# 
# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
# 
# raw_data_mcc <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,51,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
# }
# 
# d_raw_mcc <-raw_data_mcc %>%
#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
#          test_date = as.Date(test_date))
# 
# 
# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# 
# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          leftObject = leftFruit,
#          rightObject = rightFruit, 
#          pick = str_sub(pick,72,str_length(pick)-4),
#          agent = ifelse(speakerChange == "false", agent,altAgent),
#          experiment = "dis_novelty_mcc")%>%
#   filter(speakerChange == "false", trial != "train")%>%
#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
# 
# 
# # join datasets
# 
# d <- bind_rows(d_spin, d_mcc)
# 
# write_csv(d_spin, "../data/novelty.csv")
# #write_csv(d, "../data/child_novelty.csv")

d <- read_csv("../data/novelty.csv")%>%
  mutate(subage = factor(subage))

@@

@@

ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
  geom_smooth(data = d_spin, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.01)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion novel item chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F, col = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()

ggsave("../graphs/novelty.png", width = 5, height = 3, scale = 1.2)
```
